Run-Time Monitoring with Adjustable Overhead \\Using Dataflow-Guided Filtering

### 2015-01-05 evaluation.tex
Updated full overhead of LS.

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 2.6-9.8x with an average of 5.7x.
For BC, normalized execution
are 2.7x on average and range from 1.02x to 13.6x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would observe higher overheads. IMP shows normalized
execution times of 1.6-9.5x with an average of 5.8x. Overheads for LS (not pictured)
applied to the SPLASH-2 benchmarks are
1.03-1.29x after null metadata filtering and the average
overhead observed is 1.13x.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

>>>>

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 2.6-9.8x with an average of 5.7x.
For BC, normalized execution
are 2.7x on average and range from 1.02x to 13.6x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 1.1x slowdown with a maximum slowdown of 1.3x with null
metadata filtering. This low overhead is due to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would observe higher overheads. IMP shows normalized
execution times of 1.6-9.5x with an average of 5.8x. Overheads for LS (not pictured)
applied to the SPLASH-2 benchmarks are
1.04-1.29x after null metadata filtering and the average
overhead observed is 1.13x.
Our baseline system and overheads are similar to previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we also evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.
